
#Load - 2 weeks performance period (f_Target_2w)


```{r}
# continuous
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m00_2w_logit_base.rda")
# load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m01_2w_logit_all.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m02_2w_logit_penalized.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m03_2w_rpart.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m04_2w_RF.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m05_2w_pcr.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m06_2w_GBM.rda")

# factor
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m10_2w_logit_base_factor.rda")
# load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m11_2w_logit_all_factor.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m12_2w_logit_penalized_facor.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m13_2w_rpart_factor.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m14_2w_RF_factor.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m15_2w_pcr_factor.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m16_2w_GBM_factor.rda")

# log
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m20_2w_logit_base_log.rda")
# load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m21_2w_logit_all_log.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m22_2w_logit_penalized_log.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m23_2w_rpart_log.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m24_2w_RF_log.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m25_2w_pcr_log.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m26_2w_GBM_log.rda")
```


#2 weeks performance period (f_Target_2w)

##2w continuous

m00_2w_logit_base
```{r}

# test data
m00_2w_test_pred <- predict.train(m00_2w_logit_base, newdata = JZ_test, type = "prob")
m00_2w_pred_test <- prediction(m00_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m00_2w_perf_test <- performance(m00_2w_pred_test, measure = "tpr", x.measure = "fpr")
m00_2w_AUC_test <- performance(m00_2w_pred_test, measure = "auc")@y.values[[1]]
m00_2w_roc_df_test <- data.table(
  model = "m00_2w_logit_base",
  FPR = m00_2w_perf_test@x.values[[1]],
  TPR = m00_2w_perf_test@y.values[[1]],
  cutoff = m00_2w_perf_test@alpha.values[[1]])

# external data
m00_2w_external_pred <- predict.train(m00_2w_logit_base, newdata = JZ_external, type = "prob")
m00_2w_pred_external <- prediction(m00_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m00_2w_perf_external <- performance(m00_2w_pred_external, measure = "tpr", x.measure = "fpr")
m00_2w_AUC_external <- performance(m00_2w_pred_external, measure = "auc")@y.values[[1]]
m00_2w_roc_df_external <- data.table(
  model = "m00_2w_logit_base",
  FPR = m00_2w_perf_external@x.values[[1]],
  TPR = m00_2w_perf_external@y.values[[1]],
  cutoff = m00_2w_perf_external@alpha.values[[1]])

# las resultas
  # coef(m00_2w_logit_base$finalModel)
m00_2w_logit_base$results$ROC
m00_2w_AUC_test
m00_2w_AUC_external

```


m01_2w_logit_all
```{r}

# # test data
# m01_2w_test_pred <- predict.train(m01_2w_logit_all, newdata = JZ_test, type = "prob")
# m01_2w_pred_test <- prediction(m01_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
# m01_2w_perf_test <- performance(m01_2w_pred_test, measure = "tpr", x.measure = "fpr")
# m01_2w_AUC_test <- performance(m01_2w_pred_test, measure = "auc")@y.values[[1]]
# m01_2w_roc_df_test <- data.table(
#   model = "m01_2w_logit_all",
#   FPR = m01_2w_perf_test@x.values[[1]],
#   TPR = m01_2w_perf_test@y.values[[1]],
#   cutoff = m01_2w_perf_test@alpha.values[[1]])
# 
# # external data
# m01_2w_external_pred <- predict.train(m01_2w_logit_all, newdata = JZ_external, type = "prob")
# m01_2w_pred_external <- prediction(m01_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
# m01_2w_perf_external <- performance(m01_2w_pred_external, measure = "tpr", x.measure = "fpr")
# m01_2w_AUC_external <- performance(m01_2w_pred_external, measure = "auc")@y.values[[1]]
# m01_2w_roc_df_external <- data.table(
#   model = "m01_2w_logit_all",
#   FPR = m01_2w_perf_external@x.values[[1]],
#   TPR = m01_2w_perf_external@y.values[[1]],
#   cutoff = m01_2w_perf_external@alpha.values[[1]])
# 
# # las resultas
#   #coef(m01_2w_logit_all$finalModel)
# m01_2w_logit_all$results$ROC
# m01_2w_AUC_test
# m01_2w_AUC_external

```

m02_2w_logit_penalized
```{r}

# test data
m02_2w_test_pred <- predict.train(m02_2w_logit_penalized, newdata = JZ_test, type = "prob")
m02_2w_pred_test <- prediction(m02_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m02_2w_perf_test <- performance(m02_2w_pred_test, measure = "tpr", x.measure = "fpr")
m02_2w_AUC_test <- performance(m02_2w_pred_test, measure = "auc")@y.values[[1]]
m02_2w_roc_df_test <- data.table(
  model = "m02_2w_logit_penalized",
  FPR = m02_2w_perf_test@x.values[[1]],
  TPR = m02_2w_perf_test@y.values[[1]],
  cutoff = m02_2w_perf_test@alpha.values[[1]])

# external data
m02_2w_external_pred <- predict.train(m02_2w_logit_penalized, newdata = JZ_external, type = "prob")
m02_2w_pred_external <- prediction(m02_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m02_2w_perf_external <- performance(m02_2w_pred_external, measure = "tpr", x.measure = "fpr")
m02_2w_AUC_external <- performance(m02_2w_pred_external, measure = "auc")@y.values[[1]]
m02_2w_roc_df_external <- data.table(
  model = "m02_2w_logit_penalized",
  FPR = m02_2w_perf_external@x.values[[1]],
  TPR = m02_2w_perf_external@y.values[[1]],
  cutoff = m02_2w_perf_external@alpha.values[[1]])

# las resultas
  #coef(m02_2w_logit_penalized$finalModel)
m02_2w_logit_penalized$results$ROC
m02_2w_AUC_test
m02_2w_AUC_external
```

m03_2w_rpart
```{r}

# test data
m03_2w_test_pred <- predict.train(m03_2w_rpart, newdata = JZ_test, type = "prob")
m03_2w_pred_test <- prediction(m03_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m03_2w_perf_test <- performance(m03_2w_pred_test, measure = "tpr", x.measure = "fpr")
m03_2w_AUC_test <- performance(m03_2w_pred_test, measure = "auc")@y.values[[1]]
m03_2w_roc_df_test <- data.table(
  model = "m03_2w_rpart",
  FPR = m03_2w_perf_test@x.values[[1]],
  TPR = m03_2w_perf_test@y.values[[1]],
  cutoff = m03_2w_perf_test@alpha.values[[1]])

# external data
m03_2w_external_pred <- predict.train(m03_2w_rpart, newdata = JZ_external, type = "prob")
m03_2w_pred_external <- prediction(m03_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m03_2w_perf_external <- performance(m03_2w_pred_external, measure = "tpr", x.measure = "fpr")
m03_2w_AUC_external <- performance(m03_2w_pred_external, measure = "auc")@y.values[[1]]
m03_2w_roc_df_external <- data.table(
  model = "m03_2w_rpart",
  FPR = m03_2w_perf_external@x.values[[1]],
  TPR = m03_2w_perf_external@y.values[[1]],
  cutoff = m03_2w_perf_external@alpha.values[[1]])

# las resultas
m03_2w_rpart$results$ROC
m03_2w_AUC_test
m03_2w_AUC_external
```

m04_2w_RF
```{r}

# test data
m04_2w_test_pred <- predict.train(m04_2w_RF, newdata = JZ_test, type = "prob")
m04_2w_pred_test <- prediction(m04_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m04_2w_perf_test <- performance(m04_2w_pred_test, measure = "tpr", x.measure = "fpr")
m04_2w_AUC_test <- performance(m04_2w_pred_test, measure = "auc")@y.values[[1]]
m04_2w_roc_df_test <- data.table(
  model = "m04_2w_RF",
  FPR = m04_2w_perf_test@x.values[[1]],
  TPR = m04_2w_perf_test@y.values[[1]],
  cutoff = m04_2w_perf_test@alpha.values[[1]])

# external data
m04_2w_external_pred <- predict.train(m04_2w_RF, newdata = JZ_external, type = "prob")
m04_2w_pred_external <- prediction(m04_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m04_2w_perf_external <- performance(m04_2w_pred_external, measure = "tpr", x.measure = "fpr")
m04_2w_AUC_external <- performance(m04_2w_pred_external, measure = "auc")@y.values[[1]]
m04_2w_roc_df_external <- data.table(
  model = "m04_2w_RF",
  FPR = m04_2w_perf_external@x.values[[1]],
  TPR = m04_2w_perf_external@y.values[[1]],
  cutoff = m04_2w_perf_external@alpha.values[[1]])

# las resultas
varImp(m04_2w_RF, scale = FALSE)
m04_2w_RF$results$ROC
m04_2w_AUC_test
m04_2w_AUC_external
```

m05_2w_pcr
```{r}

# test data
m05_2w_test_pred <- predict.train(m05_2w_pcr, newdata = JZ_test, type = "prob")
m05_2w_pred_test <- prediction(m05_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m05_2w_perf_test <- performance(m05_2w_pred_test, measure = "tpr", x.measure = "fpr")
m05_2w_AUC_test <- performance(m05_2w_pred_test, measure = "auc")@y.values[[1]]
m05_2w_roc_df_test <- data.table(
  model = "m05_2w_pcr",
  FPR = m05_2w_perf_test@x.values[[1]],
  TPR = m05_2w_perf_test@y.values[[1]],
  cutoff = m05_2w_perf_test@alpha.values[[1]])

m05_2w_external_pred <- predict.train(m05_2w_pcr, newdata = JZ_external, type = "prob")
m05_2w_pred_external <- prediction(m05_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m05_2w_perf_external <- performance(m05_2w_pred_external, measure = "tpr", x.measure = "fpr")
m05_2w_AUC_external <- performance(m05_2w_pred_external, measure = "auc")@y.values[[1]]
m05_2w_roc_df_external <- data.table(
  model = "m05_2w_pcr",
  FPR = m05_2w_perf_external@x.values[[1]],
  TPR = m05_2w_perf_external@y.values[[1]],
  cutoff = m05_2w_perf_external@alpha.values[[1]])

# las resultas
#coef(m05_2w_pcr$finalModel)
m05_2w_pcr$results$ROC
m05_2w_AUC_test
m05_2w_AUC_external
```

m06_2w_GBM
```{r}
# test data
m06_2w_test_pred <- predict.train(m06_2w_GBM, newdata = JZ_test, type = "prob")
m06_2w_pred_test <- prediction(m06_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m06_2w_perf_test <- performance(m06_2w_pred_test, measure = "tpr", x.measure = "fpr")
m06_2w_AUC_test <- performance(m06_2w_pred_test, measure = "auc")@y.values[[1]]
m06_2w_roc_df_test <- data.table(
  model = "m06_2w_GBM",
  FPR = m06_2w_perf_test@x.values[[1]],
  TPR = m06_2w_perf_test@y.values[[1]],
  cutoff = m06_2w_perf_test@alpha.values[[1]])

# external data
m06_2w_external_pred <- predict.train(m06_2w_GBM, newdata = JZ_external, type = "prob")
m06_2w_pred_external <- prediction(m06_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m06_2w_perf_external <- performance(m06_2w_pred_external, measure = "tpr", x.measure = "fpr")
m06_2w_AUC_external <- performance(m06_2w_pred_external, measure = "auc")@y.values[[1]]
m06_2w_roc_df_external <- data.table(
  model = "m06_2w_GBM",
  FPR = m06_2w_perf_external@x.values[[1]],
  TPR = m06_2w_perf_external@y.values[[1]],
  cutoff = m06_2w_perf_external@alpha.values[[1]])

# las resultas
#coef(m06_2w_GBM$finalModel)
m06_2w_GBM$results$ROC
m06_2w_AUC_test
m06_2w_AUC_external
```


##2w factor

m10_2w_logit_base_factor
```{r}
# test data
m10_2w_test_pred <- predict.train(m10_2w_logit_base_factor, newdata = JZ_test, type = "prob")
m10_2w_pred_test <- prediction(m10_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m10_2w_perf_test <- performance(m10_2w_pred_test, measure = "tpr", x.measure = "fpr")
m10_2w_AUC_test <- performance(m10_2w_pred_test, measure = "auc")@y.values[[1]]
m10_2w_roc_df_test <- data.table(
  model = "m10_2w_logit_base_factor",
  FPR = m10_2w_perf_test@x.values[[1]],
  TPR = m10_2w_perf_test@y.values[[1]],
  cutoff = m10_2w_perf_test@alpha.values[[1]])

# external data
m10_2w_external_pred <- predict.train(m10_2w_logit_base_factor, newdata = JZ_external, type = "prob")
m10_2w_pred_external <- prediction(m10_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m10_2w_perf_external <- performance(m10_2w_pred_external, measure = "tpr", x.measure = "fpr")
m10_2w_AUC_external <- performance(m10_2w_pred_external, measure = "auc")@y.values[[1]]
m10_2w_roc_df_external <- data.table(
  model = "m10_2w_logit_base_factor",
  FPR = m10_2w_perf_external@x.values[[1]],
  TPR = m10_2w_perf_external@y.values[[1]],
  cutoff = m10_2w_perf_external@alpha.values[[1]])

# las resultas
  # coef(m10_2w_logit_base_factor$finalModel)
m10_2w_logit_base_factor$results$ROC
m10_2w_AUC_test
m10_2w_AUC_external

```


m11_2w_logit_all_factor
```{r}
# # test data
# m11_2w_test_pred <- predict.train(m11_2w_logit_all_factor, newdata = JZ_test, type = "prob")
# m11_2w_pred_test <- prediction(m11_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
# m11_2w_perf_test <- performance(m11_2w_pred_test, measure = "tpr", x.measure = "fpr")
# m11_2w_AUC_test <- performance(m11_2w_pred_test, measure = "auc")@y.values[[1]]
# m11_2w_roc_df_test <- data.table(
#   model = "m11_2w_logit_all_factor",
#   FPR = m11_2w_perf_test@x.values[[1]],
#   TPR = m11_2w_perf_test@y.values[[1]],
#   cutoff = m11_2w_perf_test@alpha.values[[1]])
# 
# # external data
# m11_2w_external_pred <- predict.train(m11_2w_logit_all_factor, newdata = JZ_external, type = "prob")
# m11_2w_pred_external <- prediction(m11_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
# m11_2w_perf_external <- performance(m11_2w_pred_external, measure = "tpr", x.measure = "fpr")
# m11_2w_AUC_external <- performance(m11_2w_pred_external, measure = "auc")@y.values[[1]]
# m11_2w_roc_df_external <- data.table(
#   model = "m11_2w_logit_all_factor",
#   FPR = m11_2w_perf_external@x.values[[1]],
#   TPR = m11_2w_perf_external@y.values[[1]],
#   cutoff = m11_2w_perf_external@alpha.values[[1]])
# 
# # las resultas
#   #coef(m11_2w_logit_all_factor$finalModel)
# m11_2w_logit_all_factor$results$ROC
# m11_2w_AUC_test
# m11_2w_AUC_external

```

m12_2w_logit_penalized_facor
```{r}
# test data
m12_2w_test_pred <- predict.train(m12_2w_logit_penalized_facor, newdata = JZ_test, type = "prob")
m12_2w_pred_test <- prediction(m12_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m12_2w_perf_test <- performance(m12_2w_pred_test, measure = "tpr", x.measure = "fpr")
m12_2w_AUC_test <- performance(m12_2w_pred_test, measure = "auc")@y.values[[1]]
m12_2w_roc_df_test <- data.table(
  model = "m12_2w_logit_penalized_facor",
  FPR = m12_2w_perf_test@x.values[[1]],
  TPR = m12_2w_perf_test@y.values[[1]],
  cutoff = m12_2w_perf_test@alpha.values[[1]])

# external data
m12_2w_external_pred <- predict.train(m12_2w_logit_penalized_facor, newdata = JZ_external, type = "prob")
m12_2w_pred_external <- prediction(m12_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m12_2w_perf_external <- performance(m12_2w_pred_external, measure = "tpr", x.measure = "fpr")
m12_2w_AUC_external <- performance(m12_2w_pred_external, measure = "auc")@y.values[[1]]
m12_2w_roc_df_external <- data.table(
  model = "m12_2w_logit_penalized_facor",
  FPR = m12_2w_perf_external@x.values[[1]],
  TPR = m12_2w_perf_external@y.values[[1]],
  cutoff = m12_2w_perf_external@alpha.values[[1]])

# las resultas
  #coef(m12_2w_logit_penalized_facor$finalModel)
m12_2w_logit_penalized_facor$results$ROC
m12_2w_AUC_test
m12_2w_AUC_external
```

m13_2w_rpart_factor
```{r}
# test data
m13_2w_test_pred <- predict.train(m13_2w_rpart_factor, newdata = JZ_test, type = "prob")
m13_2w_pred_test <- prediction(m13_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m13_2w_perf_test <- performance(m13_2w_pred_test, measure = "tpr", x.measure = "fpr")
m13_2w_AUC_test <- performance(m13_2w_pred_test, measure = "auc")@y.values[[1]]
m13_2w_roc_df_test <- data.table(
  model = "m13_2w_rpart_factor",
  FPR = m13_2w_perf_test@x.values[[1]],
  TPR = m13_2w_perf_test@y.values[[1]],
  cutoff = m13_2w_perf_test@alpha.values[[1]])

# external data
m13_2w_external_pred <- predict.train(m13_2w_rpart_factor, newdata = JZ_external, type = "prob")
m13_2w_pred_external <- prediction(m13_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m13_2w_perf_external <- performance(m13_2w_pred_external, measure = "tpr", x.measure = "fpr")
m13_2w_AUC_external <- performance(m13_2w_pred_external, measure = "auc")@y.values[[1]]
m13_2w_roc_df_external <- data.table(
  model = "m13_2w_rpart_factor",
  FPR = m13_2w_perf_external@x.values[[1]],
  TPR = m13_2w_perf_external@y.values[[1]],
  cutoff = m13_2w_perf_external@alpha.values[[1]])

# las resultas
m13_2w_rpart_factor$results$ROC
m13_2w_AUC_test
m13_2w_AUC_external
```

m14_2w_RF_factor
```{r}
# test data
m14_2w_test_pred <- predict.train(m14_2w_RF_factor, newdata = JZ_test, type = "prob")
m14_2w_pred_test <- prediction(m14_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m14_2w_perf_test <- performance(m14_2w_pred_test, measure = "tpr", x.measure = "fpr")
m14_2w_AUC_test <- performance(m14_2w_pred_test, measure = "auc")@y.values[[1]]
m14_2w_roc_df_test <- data.table(
  model = "m14_2w_RF_factor",
  FPR = m14_2w_perf_test@x.values[[1]],
  TPR = m14_2w_perf_test@y.values[[1]],
  cutoff = m14_2w_perf_test@alpha.values[[1]])

# external data
m14_2w_external_pred <- predict.train(m14_2w_RF_factor, newdata = JZ_external, type = "prob")
m14_2w_pred_external <- prediction(m14_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m14_2w_perf_external <- performance(m14_2w_pred_external, measure = "tpr", x.measure = "fpr")
m14_2w_AUC_external <- performance(m14_2w_pred_external, measure = "auc")@y.values[[1]]
m14_2w_roc_df_external <- data.table(
  model = "m14_2w_RF_factor",
  FPR = m14_2w_perf_external@x.values[[1]],
  TPR = m14_2w_perf_external@y.values[[1]],
  cutoff = m14_2w_perf_external@alpha.values[[1]])

# las resultas
varImp(m14_2w_RF_factor, scale = FALSE)
m14_2w_RF_factor$results$ROC
m14_2w_AUC_test
m14_2w_AUC_external
```

m15_2w_pcr_factor
```{r}
# test data
m15_2w_test_pred <- predict.train(m15_2w_pcr_factor, newdata = JZ_test, type = "prob")
m15_2w_pred_test <- prediction(m15_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m15_2w_perf_test <- performance(m15_2w_pred_test, measure = "tpr", x.measure = "fpr")
m15_2w_AUC_test <- performance(m15_2w_pred_test, measure = "auc")@y.values[[1]]
m15_2w_roc_df_test <- data.table(
  model = "m15_2w_pcr_factor",
  FPR = m15_2w_perf_test@x.values[[1]],
  TPR = m15_2w_perf_test@y.values[[1]],
  cutoff = m15_2w_perf_test@alpha.values[[1]])

m15_2w_external_pred <- predict.train(m15_2w_pcr_factor, newdata = JZ_external, type = "prob")
m15_2w_pred_external <- prediction(m15_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m15_2w_perf_external <- performance(m15_2w_pred_external, measure = "tpr", x.measure = "fpr")
m15_2w_AUC_external <- performance(m15_2w_pred_external, measure = "auc")@y.values[[1]]
m15_2w_roc_df_external <- data.table(
  model = "m15_2w_pcr_factor",
  FPR = m15_2w_perf_external@x.values[[1]],
  TPR = m15_2w_perf_external@y.values[[1]],
  cutoff = m15_2w_perf_external@alpha.values[[1]])

# las resultas
#coef(m15_2w_pcr_factor$finalModel)
m15_2w_pcr_factor$results$ROC
m15_2w_AUC_test
m15_2w_AUC_external
```

m16_2w_GBM_factor
```{r}

# test data
m16_2w_test_pred <- predict.train(m16_2w_GBM_factor, newdata = JZ_test, type = "prob")
m16_2w_pred_test <- prediction(m16_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m16_2w_perf_test <- performance(m16_2w_pred_test, measure = "tpr", x.measure = "fpr")
m16_2w_AUC_test <- performance(m16_2w_pred_test, measure = "auc")@y.values[[1]]
m16_2w_roc_df_test <- data.table(
  model = "m16_2w_GBM_factor",
  FPR = m16_2w_perf_test@x.values[[1]],
  TPR = m16_2w_perf_test@y.values[[1]],
  cutoff = m16_2w_perf_test@alpha.values[[1]])

m16_2w_external_pred <- predict.train(m16_2w_GBM_factor, newdata = JZ_external, type = "prob")
m16_2w_pred_external <- prediction(m16_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m16_2w_perf_external <- performance(m16_2w_pred_external, measure = "tpr", x.measure = "fpr")
m16_2w_AUC_external <- performance(m16_2w_pred_external, measure = "auc")@y.values[[1]]
m16_2w_roc_df_external <- data.table(
  model = "m16_2w_GBM_factor",
  FPR = m16_2w_perf_external@x.values[[1]],
  TPR = m16_2w_perf_external@y.values[[1]],
  cutoff = m16_2w_perf_external@alpha.values[[1]])

# las resultas
#coef(m16_2w_GBM_factor$finalModel)
m16_2w_GBM_factor$results$ROC
m16_2w_AUC_test
m16_2w_AUC_external

```

##2w log

m20_2w_logit_base_log
```{r}
# test data
m20_2w_test_pred <- predict.train(m20_2w_logit_base_log, newdata = JZ_test, type = "prob")
m20_2w_pred_test <- prediction(m20_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m20_2w_perf_test <- performance(m20_2w_pred_test, measure = "tpr", x.measure = "fpr")
m20_2w_AUC_test <- performance(m20_2w_pred_test, measure = "auc")@y.values[[1]]
m20_2w_roc_df_test <- data.table(
  model = "m20_2w_logit_base_log",
  FPR = m20_2w_perf_test@x.values[[1]],
  TPR = m20_2w_perf_test@y.values[[1]],
  cutoff = m20_2w_perf_test@alpha.values[[1]])

# external data
m20_2w_external_pred <- predict.train(m20_2w_logit_base_log, newdata = JZ_external, type = "prob")
m20_2w_pred_external <- prediction(m20_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m20_2w_perf_external <- performance(m20_2w_pred_external, measure = "tpr", x.measure = "fpr")
m20_2w_AUC_external <- performance(m20_2w_pred_external, measure = "auc")@y.values[[1]]
m20_2w_roc_df_external <- data.table(
  model = "m20_2w_logit_base_log",
  FPR = m20_2w_perf_external@x.values[[1]],
  TPR = m20_2w_perf_external@y.values[[1]],
  cutoff = m20_2w_perf_external@alpha.values[[1]])

# las resultas
  # coef(m20_2w_logit_base_log$finalModel)
m20_2w_logit_base_log$results$ROC
m20_2w_AUC_test
m20_2w_AUC_external

```


m21_2w_logit_all_log
```{r}
# # test data
# m21_2w_test_pred <- predict.train(m21_2w_logit_all_log, newdata = JZ_test, type = "prob")
# m21_2w_pred_test <- prediction(m21_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
# m21_2w_perf_test <- performance(m21_2w_pred_test, measure = "tpr", x.measure = "fpr")
# m21_2w_AUC_test <- performance(m21_2w_pred_test, measure = "auc")@y.values[[1]]
# m21_2w_roc_df_test <- data.table(
#   model = "m21_2w_logit_all_log",
#   FPR = m21_2w_perf_test@x.values[[1]],
#   TPR = m21_2w_perf_test@y.values[[1]],
#   cutoff = m21_2w_perf_test@alpha.values[[1]])
# 
# # external data
# m21_2w_external_pred <- predict.train(m21_2w_logit_all_log, newdata = JZ_external, type = "prob")
# m21_2w_pred_external <- prediction(m21_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
# m21_2w_perf_external <- performance(m21_2w_pred_external, measure = "tpr", x.measure = "fpr")
# m21_2w_AUC_external <- performance(m21_2w_pred_external, measure = "auc")@y.values[[1]]
# m21_2w_roc_df_external <- data.table(
#   model = "m21_2w_logit_all_log",
#   FPR = m21_2w_perf_external@x.values[[1]],
#   TPR = m21_2w_perf_external@y.values[[1]],
#   cutoff = m21_2w_perf_external@alpha.values[[1]])
# 
# # las resultas
#   #coef(m21_2w_logit_all_log$finalModel)
# m21_2w_logit_all_log$results$ROC
# m21_2w_AUC_test
# m21_2w_AUC_external

```

m22_2w_logit_penalized_log
```{r}
# test data
m22_2w_test_pred <- predict.train(m22_2w_logit_penalized_log, newdata = JZ_test, type = "prob")
m22_2w_pred_test <- prediction(m22_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m22_2w_perf_test <- performance(m22_2w_pred_test, measure = "tpr", x.measure = "fpr")
m22_2w_AUC_test <- performance(m22_2w_pred_test, measure = "auc")@y.values[[1]]
m22_2w_roc_df_test <- data.table(
  model = "m22_2w_logit_penalized_log",
  FPR = m22_2w_perf_test@x.values[[1]],
  TPR = m22_2w_perf_test@y.values[[1]],
  cutoff = m22_2w_perf_test@alpha.values[[1]])

# external data
m22_2w_external_pred <- predict.train(m22_2w_logit_penalized_log, newdata = JZ_external, type = "prob")
m22_2w_pred_external <- prediction(m22_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m22_2w_perf_external <- performance(m22_2w_pred_external, measure = "tpr", x.measure = "fpr")
m22_2w_AUC_external <- performance(m22_2w_pred_external, measure = "auc")@y.values[[1]]
m22_2w_roc_df_external <- data.table(
  model = "m22_2w_logit_penalized_log",
  FPR = m22_2w_perf_external@x.values[[1]],
  TPR = m22_2w_perf_external@y.values[[1]],
  cutoff = m22_2w_perf_external@alpha.values[[1]])

# las resultas
  #coef(m22_2w_logit_penalized_log$finalModel)
m22_2w_logit_penalized_log$results$ROC
m22_2w_AUC_test
m22_2w_AUC_external
```

m23_2w_rpart_log
```{r}
# test data
m23_2w_test_pred <- predict.train(m23_2w_rpart_log, newdata = JZ_test, type = "prob")
m23_2w_pred_test <- prediction(m23_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m23_2w_perf_test <- performance(m23_2w_pred_test, measure = "tpr", x.measure = "fpr")
m23_2w_AUC_test <- performance(m23_2w_pred_test, measure = "auc")@y.values[[1]]
m23_2w_roc_df_test <- data.table(
  model = "m23_2w_rpart_log",
  FPR = m23_2w_perf_test@x.values[[1]],
  TPR = m23_2w_perf_test@y.values[[1]],
  cutoff = m23_2w_perf_test@alpha.values[[1]])

# external data
m23_2w_external_pred <- predict.train(m23_2w_rpart_log, newdata = JZ_external, type = "prob")
m23_2w_pred_external <- prediction(m23_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m23_2w_perf_external <- performance(m23_2w_pred_external, measure = "tpr", x.measure = "fpr")
m23_2w_AUC_external <- performance(m23_2w_pred_external, measure = "auc")@y.values[[1]]
m23_2w_roc_df_external <- data.table(
  model = "m23_2w_rpart_log",
  FPR = m23_2w_perf_external@x.values[[1]],
  TPR = m23_2w_perf_external@y.values[[1]],
  cutoff = m23_2w_perf_external@alpha.values[[1]])

# las resultas
m23_2w_rpart_log$results$ROC
m23_2w_AUC_test
m23_2w_AUC_external
```

m24_2w_RF_log
```{r}
# test data
m24_2w_test_pred <- predict.train(m24_2w_RF_log, newdata = JZ_test, type = "prob")
m24_2w_pred_test <- prediction(m24_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m24_2w_perf_test <- performance(m24_2w_pred_test, measure = "tpr", x.measure = "fpr")
m24_2w_AUC_test <- performance(m24_2w_pred_test, measure = "auc")@y.values[[1]]
m24_2w_roc_df_test <- data.table(
  model = "m24_2w_RF_log",
  FPR = m24_2w_perf_test@x.values[[1]],
  TPR = m24_2w_perf_test@y.values[[1]],
  cutoff = m24_2w_perf_test@alpha.values[[1]])

# external data
m24_2w_external_pred <- predict.train(m24_2w_RF_log, newdata = JZ_external, type = "prob")
m24_2w_pred_external <- prediction(m24_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m24_2w_perf_external <- performance(m24_2w_pred_external, measure = "tpr", x.measure = "fpr")
m24_2w_AUC_external <- performance(m24_2w_pred_external, measure = "auc")@y.values[[1]]
m24_2w_roc_df_external <- data.table(
  model = "m24_2w_RF_log",
  FPR = m24_2w_perf_external@x.values[[1]],
  TPR = m24_2w_perf_external@y.values[[1]],
  cutoff = m24_2w_perf_external@alpha.values[[1]])

# las resultas
varImp(m24_2w_RF_log, scale = FALSE)
m24_2w_RF_log$results$ROC
m24_2w_AUC_test
m24_2w_AUC_external
```

m25_2w_pcr_log
```{r}
# test data
m25_2w_test_pred <- predict.train(m25_2w_pcr_log, newdata = JZ_test, type = "prob")
m25_2w_pred_test <- prediction(m25_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m25_2w_perf_test <- performance(m25_2w_pred_test, measure = "tpr", x.measure = "fpr")
m25_2w_AUC_test <- performance(m25_2w_pred_test, measure = "auc")@y.values[[1]]
m25_2w_roc_df_test <- data.table(
  model = "m25_2w_pcr_log",
  FPR = m25_2w_perf_test@x.values[[1]],
  TPR = m25_2w_perf_test@y.values[[1]],
  cutoff = m25_2w_perf_test@alpha.values[[1]])

m25_2w_external_pred <- predict.train(m25_2w_pcr_log, newdata = JZ_external, type = "prob")
m25_2w_pred_external <- prediction(m25_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m25_2w_perf_external <- performance(m25_2w_pred_external, measure = "tpr", x.measure = "fpr")
m25_2w_AUC_external <- performance(m25_2w_pred_external, measure = "auc")@y.values[[1]]
m25_2w_roc_df_external <- data.table(
  model = "m25_2w_pcr_log",
  FPR = m25_2w_perf_external@x.values[[1]],
  TPR = m25_2w_perf_external@y.values[[1]],
  cutoff = m25_2w_perf_external@alpha.values[[1]])

# las resultas
#coef(m25_2w_pcr_log$finalModel)
m25_2w_pcr_log$results$ROC
m25_2w_AUC_test
m25_2w_AUC_external
```

m26_2w_GBM_log
```{r}
# test data
m26_2w_test_pred <- predict.train(m26_2w_GBM_log, newdata = JZ_test, type = "prob")
m26_2w_pred_test <- prediction(m26_2w_test_pred$Y, JZ_test[["f_Target_2w"]])
m26_2w_perf_test <- performance(m26_2w_pred_test, measure = "tpr", x.measure = "fpr")
m26_2w_AUC_test <- performance(m26_2w_pred_test, measure = "auc")@y.values[[1]]
m26_2w_roc_df_test <- data.table(
  model = "m26_2w_GBM_log",
  FPR = m26_2w_perf_test@x.values[[1]],
  TPR = m26_2w_perf_test@y.values[[1]],
  cutoff = m26_2w_perf_test@alpha.values[[1]])

m26_2w_external_pred <- predict.train(m26_2w_GBM_log, newdata = JZ_external, type = "prob")
m26_2w_pred_external <- prediction(m26_2w_external_pred$Y, JZ_external[["f_Target_2w"]])
m26_2w_perf_external <- performance(m26_2w_pred_external, measure = "tpr", x.measure = "fpr")
m26_2w_AUC_external <- performance(m26_2w_pred_external, measure = "auc")@y.values[[1]]
m26_2w_roc_df_external <- data.table(
  model = "m26_2w_GBM_log",
  FPR = m26_2w_perf_external@x.values[[1]],
  TPR = m26_2w_perf_external@y.values[[1]],
  cutoff = m26_2w_perf_external@alpha.values[[1]])

# las resultas
#coef(m26_2w_GBM_log$finalModel)
m26_2w_GBM_log$results$ROC
m26_2w_AUC_test
m26_2w_AUC_external

```


deleting what is not needed
```{r}
rm(m00_2w_test_pred, m00_2w_pred_test, m00_2w_perf_test, m00_2w_external_pred, m00_2w_pred_external, m00_2w_perf_external)
rm(m02_2w_test_pred, m02_2w_pred_test, m02_2w_perf_test, m02_2w_external_pred, m02_2w_pred_external, m02_2w_perf_external)
rm(m04_2w_test_pred, m04_2w_pred_test, m04_2w_perf_test, m04_2w_external_pred, m04_2w_pred_external, m04_2w_perf_external)
rm(m05_2w_test_pred, m05_2w_pred_test, m05_2w_perf_test, m05_2w_external_pred, m05_2w_pred_external, m05_2w_perf_external)
rm(m06_2w_test_pred, m06_2w_pred_test, m06_2w_perf_test, m06_2w_external_pred, m06_2w_pred_external, m06_2w_perf_external)
rm(m10_2w_test_pred, m10_2w_pred_test, m10_2w_perf_test, m10_2w_external_pred, m10_2w_pred_external, m10_2w_perf_external)
rm(m12_2w_test_pred, m12_2w_pred_test, m12_2w_perf_test, m12_2w_external_pred, m12_2w_pred_external, m12_2w_perf_external)
rm(m14_2w_test_pred, m14_2w_pred_test, m14_2w_perf_test, m14_2w_external_pred, m14_2w_pred_external, m14_2w_perf_external)
rm(m15_2w_test_pred, m15_2w_pred_test, m15_2w_perf_test, m15_2w_external_pred, m15_2w_pred_external, m15_2w_perf_external)
rm(m16_2w_test_pred, m16_2w_pred_test, m16_2w_perf_test, m16_2w_external_pred, m16_2w_pred_external, m16_2w_perf_external)
rm(m20_2w_test_pred, m20_2w_pred_test, m20_2w_perf_test, m20_2w_external_pred, m20_2w_pred_external, m20_2w_perf_external)
rm(m22_2w_test_pred, m22_2w_pred_test, m22_2w_perf_test, m22_2w_external_pred, m22_2w_pred_external, m22_2w_perf_external)
rm(m24_2w_test_pred, m24_2w_pred_test, m24_2w_perf_test, m24_2w_external_pred, m24_2w_pred_external, m24_2w_perf_external)
rm(m25_2w_test_pred, m25_2w_pred_test, m25_2w_perf_test, m25_2w_external_pred, m25_2w_pred_external, m25_2w_perf_external)
rm(m26_2w_test_pred, m26_2w_pred_test, m26_2w_perf_test, m26_2w_external_pred, m26_2w_pred_external, m26_2w_perf_external)
```

