
#Load - 1 week performance period (f_Target)


```{r}
# continuous
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m00_logit_base.rda")
#load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m01_logit_all.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m02_logit_penalized.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m03_rpart.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m04_RF.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m05_pcr.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m06_GBM.rda")

# factor
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m10_logit_base_factor.rda")
#load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m11_logit_all_factor.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m12_logit_penalized_facor.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m13_rpart_factor.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m14_RF_factor.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m15_pcr_factor.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m16_GBM_factor.rda")

# log
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m20_logit_base_log.rda")
#load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m21_logit_all_log.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m22_logit_penalized_log.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m23_rpart_log.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m24_RF_log.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m25_pcr_log.rda")
load("c:/Users/radics.gabor/Documents/icom/v07_Full_db_new/data/m26_GBM_log.rda")
```


#1 week performance period (f_Target)

##1w continuous

m00_logit_base
```{r}

# test data
m00_test_pred <- predict.train(m00_logit_base, newdata = JZ_test, type = "prob")
m00_pred_test <- prediction(m00_test_pred$Y, JZ_test[["f_Target"]])
m00_perf_test <- performance(m00_pred_test, measure = "tpr", x.measure = "fpr")
m00_AUC_test <- performance(m00_pred_test, measure = "auc")@y.values[[1]]
m00_roc_df_test <- data.table(
  model = "m00_logit_base",
  FPR = m00_perf_test@x.values[[1]],
  TPR = m00_perf_test@y.values[[1]],
  cutoff = m00_perf_test@alpha.values[[1]])

# external data
m00_external_pred <- predict.train(m00_logit_base, newdata = JZ_external, type = "prob")
m00_pred_external <- prediction(m00_external_pred$Y, JZ_external[["f_Target"]])
m00_perf_external <- performance(m00_pred_external, measure = "tpr", x.measure = "fpr")
m00_AUC_external <- performance(m00_pred_external, measure = "auc")@y.values[[1]]
m00_roc_df_external <- data.table(
  model = "m00_logit_base",
  FPR = m00_perf_external@x.values[[1]],
  TPR = m00_perf_external@y.values[[1]],
  cutoff = m00_perf_external@alpha.values[[1]])

# las resultas
  # coef(m00_logit_base$finalModel)
m00_logit_base$results$ROC
m00_AUC_test
m00_AUC_external

```


m01_logit_all
```{r}

# # test data
# m01_test_pred <- predict.train(m01_logit_all, newdata = JZ_test, type = "prob")
# m01_pred_test <- prediction(m01_test_pred$Y, JZ_test[["f_Target"]])
# m01_perf_test <- performance(m01_pred_test, measure = "tpr", x.measure = "fpr")
# m01_AUC_test <- performance(m01_pred_test, measure = "auc")@y.values[[1]]
# m01_roc_df_test <- data.table(
#   model = "m01_logit_all",
#   FPR = m01_perf_test@x.values[[1]],
#   TPR = m01_perf_test@y.values[[1]],
#   cutoff = m01_perf_test@alpha.values[[1]])
# 
# # external data
# m01_external_pred <- predict.train(m01_logit_all, newdata = JZ_external, type = "prob")
# m01_pred_external <- prediction(m01_external_pred$Y, JZ_external[["f_Target"]])
# m01_perf_external <- performance(m01_pred_external, measure = "tpr", x.measure = "fpr")
# m01_AUC_external <- performance(m01_pred_external, measure = "auc")@y.values[[1]]
# m01_roc_df_external <- data.table(
#   model = "m01_logit_all",
#   FPR = m01_perf_external@x.values[[1]],
#   TPR = m01_perf_external@y.values[[1]],
#   cutoff = m01_perf_external@alpha.values[[1]])
# 
# # las resultas
#   #coef(m01_logit_all$finalModel)
# m01_logit_all$results$ROC
# m01_AUC_test
# m01_AUC_external

```

m02_logit_penalized
```{r}

# test data
m02_test_pred <- predict.train(m02_logit_penalized, newdata = JZ_test, type = "prob")
m02_pred_test <- prediction(m02_test_pred$Y, JZ_test[["f_Target"]])
m02_perf_test <- performance(m02_pred_test, measure = "tpr", x.measure = "fpr")
m02_AUC_test <- performance(m02_pred_test, measure = "auc")@y.values[[1]]
m02_roc_df_test <- data.table(
  model = "m02_logit_penalized",
  FPR = m02_perf_test@x.values[[1]],
  TPR = m02_perf_test@y.values[[1]],
  cutoff = m02_perf_test@alpha.values[[1]])

# external data
m02_external_pred <- predict.train(m02_logit_penalized, newdata = JZ_external, type = "prob")
m02_pred_external <- prediction(m02_external_pred$Y, JZ_external[["f_Target"]])
m02_perf_external <- performance(m02_pred_external, measure = "tpr", x.measure = "fpr")
m02_AUC_external <- performance(m02_pred_external, measure = "auc")@y.values[[1]]
m02_roc_df_external <- data.table(
  model = "m02_logit_penalized",
  FPR = m02_perf_external@x.values[[1]],
  TPR = m02_perf_external@y.values[[1]],
  cutoff = m02_perf_external@alpha.values[[1]])

# las resultas
  #coef(m02_logit_penalized$finalModel)
m02_logit_penalized$results$ROC
m02_AUC_test
m02_AUC_external

```

m03_rpart
```{r}

# test data
m03_test_pred <- predict.train(m03_rpart, newdata = JZ_test, type = "prob")
m03_pred_test <- prediction(m03_test_pred$Y, JZ_test[["f_Target"]])
m03_perf_test <- performance(m03_pred_test, measure = "tpr", x.measure = "fpr")
m03_AUC_test <- performance(m03_pred_test, measure = "auc")@y.values[[1]]
m03_roc_df_test <- data.table(
  model = "m03_rpart",
  FPR = m03_perf_test@x.values[[1]],
  TPR = m03_perf_test@y.values[[1]],
  cutoff = m03_perf_test@alpha.values[[1]])

# external data
m03_external_pred <- predict.train(m03_rpart, newdata = JZ_external, type = "prob")
m03_pred_external <- prediction(m03_external_pred$Y, JZ_external[["f_Target"]])
m03_perf_external <- performance(m03_pred_external, measure = "tpr", x.measure = "fpr")
m03_AUC_external <- performance(m03_pred_external, measure = "auc")@y.values[[1]]
m03_roc_df_external <- data.table(
  model = "m03_rpart",
  FPR = m03_perf_external@x.values[[1]],
  TPR = m03_perf_external@y.values[[1]],
  cutoff = m03_perf_external@alpha.values[[1]])

# las resultas
m03_rpart$results$ROC
m03_AUC_test
m03_AUC_external


```

m04_RF
```{r}

# test data
m04_test_pred <- predict.train(m04_RF, newdata = JZ_test, type = "prob")
m04_pred_test <- prediction(m04_test_pred$Y, JZ_test[["f_Target"]])
m04_perf_test <- performance(m04_pred_test, measure = "tpr", x.measure = "fpr")
m04_AUC_test <- performance(m04_pred_test, measure = "auc")@y.values[[1]]
m04_roc_df_test <- data.table(
  model = "m04_RF",
  FPR = m04_perf_test@x.values[[1]],
  TPR = m04_perf_test@y.values[[1]],
  cutoff = m04_perf_test@alpha.values[[1]])

# external data
m04_external_pred <- predict.train(m04_RF, newdata = JZ_external, type = "prob")
m04_pred_external <- prediction(m04_external_pred$Y, JZ_external[["f_Target"]])
m04_perf_external <- performance(m04_pred_external, measure = "tpr", x.measure = "fpr")
m04_AUC_external <- performance(m04_pred_external, measure = "auc")@y.values[[1]]
m04_roc_df_external <- data.table(
  model = "m04_RF",
  FPR = m04_perf_external@x.values[[1]],
  TPR = m04_perf_external@y.values[[1]],
  cutoff = m04_perf_external@alpha.values[[1]])

# las resultas
varImp(m04_RF, scale = FALSE)
m04_RF$results$ROC
m04_AUC_test
m04_AUC_external



    ```

m05_pcr
```{r}

# test data
m05_test_pred <- predict.train(m05_pcr, newdata = JZ_test, type = "prob")
m05_pred_test <- prediction(m05_test_pred$Y, JZ_test[["f_Target"]])
m05_perf_test <- performance(m05_pred_test, measure = "tpr", x.measure = "fpr")
m05_AUC_test <- performance(m05_pred_test, measure = "auc")@y.values[[1]]
m05_roc_df_test <- data.table(
  model = "m05_pcr",
  FPR = m05_perf_test@x.values[[1]],
  TPR = m05_perf_test@y.values[[1]],
  cutoff = m05_perf_test@alpha.values[[1]])

m05_external_pred <- predict.train(m05_pcr, newdata = JZ_external, type = "prob")
m05_pred_external <- prediction(m05_external_pred$Y, JZ_external[["f_Target"]])
m05_perf_external <- performance(m05_pred_external, measure = "tpr", x.measure = "fpr")
m05_AUC_external <- performance(m05_pred_external, measure = "auc")@y.values[[1]]
m05_roc_df_external <- data.table(
  model = "m05_pcr",
  FPR = m05_perf_external@x.values[[1]],
  TPR = m05_perf_external@y.values[[1]],
  cutoff = m05_perf_external@alpha.values[[1]])

# las resultas
#coef(m05_pcr$finalModel)
m05_pcr$results$ROC
m05_AUC_test
m05_AUC_external


```


m06_GBM
```{r}
# test data
m06_test_pred <- predict.train(m06_GBM, newdata = JZ_test, type = "prob")
m06_pred_test <- prediction(m06_test_pred$Y, JZ_test[["f_Target"]])
m06_perf_test <- performance(m06_pred_test, measure = "tpr", x.measure = "fpr")
m06_AUC_test <- performance(m06_pred_test, measure = "auc")@y.values[[1]]
m06_roc_df_test <- data.table(
  model = "m06_GBM",
  FPR = m06_perf_test@x.values[[1]],
  TPR = m06_perf_test@y.values[[1]],
  cutoff = m06_perf_test@alpha.values[[1]])

# external data
m06_external_pred <- predict.train(m06_GBM, newdata = JZ_external, type = "prob")
m06_pred_external <- prediction(m06_external_pred$Y, JZ_external[["f_Target"]])
m06_perf_external <- performance(m06_pred_external, measure = "tpr", x.measure = "fpr")
m06_AUC_external <- performance(m06_pred_external, measure = "auc")@y.values[[1]]
m06_roc_df_external <- data.table(
  model = "m06_GBM",
  FPR = m06_perf_external@x.values[[1]],
  TPR = m06_perf_external@y.values[[1]],
  cutoff = m06_perf_external@alpha.values[[1]])

# las resultas
#coef(m06_GBM$finalModel)
m06_GBM$results$ROC
m06_AUC_test
m06_AUC_external


```


##1w factor

m10_logit_base_factor
```{r}
# test data
m10_test_pred <- predict.train(m10_logit_base_factor, newdata = JZ_test, type = "prob")
m10_pred_test <- prediction(m10_test_pred$Y, JZ_test[["f_Target"]])
m10_perf_test <- performance(m10_pred_test, measure = "tpr", x.measure = "fpr")
m10_AUC_test <- performance(m10_pred_test, measure = "auc")@y.values[[1]]
m10_roc_df_test <- data.table(
  model = "m10_logit_base_factor",
  FPR = m10_perf_test@x.values[[1]],
  TPR = m10_perf_test@y.values[[1]],
  cutoff = m10_perf_test@alpha.values[[1]])

# external data
m10_external_pred <- predict.train(m10_logit_base_factor, newdata = JZ_external, type = "prob")
m10_pred_external <- prediction(m10_external_pred$Y, JZ_external[["f_Target"]])
m10_perf_external <- performance(m10_pred_external, measure = "tpr", x.measure = "fpr")
m10_AUC_external <- performance(m10_pred_external, measure = "auc")@y.values[[1]]
m10_roc_df_external <- data.table(
  model = "m10_logit_base_factor",
  FPR = m10_perf_external@x.values[[1]],
  TPR = m10_perf_external@y.values[[1]],
  cutoff = m10_perf_external@alpha.values[[1]])

# las resultas
  # coef(m10_logit_base_factor$finalModel)
m10_logit_base_factor$results$ROC
m10_AUC_test
m10_AUC_external



```


m11_logit_all_factor
```{r}
# # test data
# m11_test_pred <- predict.train(m11_logit_all_factor, newdata = JZ_test, type = "prob")
# m11_pred_test <- prediction(m11_test_pred$Y, JZ_test[["f_Target"]])
# m11_perf_test <- performance(m11_pred_test, measure = "tpr", x.measure = "fpr")
# m11_AUC_test <- performance(m11_pred_test, measure = "auc")@y.values[[1]]
# m11_roc_df_test <- data.table(
#   model = "m11_logit_all_factor",
#   FPR = m11_perf_test@x.values[[1]],
#   TPR = m11_perf_test@y.values[[1]],
#   cutoff = m11_perf_test@alpha.values[[1]])
# 
# # external data
# m11_external_pred <- predict.train(m11_logit_all_factor, newdata = JZ_external, type = "prob")
# m11_pred_external <- prediction(m11_external_pred$Y, JZ_external[["f_Target"]])
# m11_perf_external <- performance(m11_pred_external, measure = "tpr", x.measure = "fpr")
# m11_AUC_external <- performance(m11_pred_external, measure = "auc")@y.values[[1]]
# m11_roc_df_external <- data.table(
#   model = "m11_logit_all_factor",
#   FPR = m11_perf_external@x.values[[1]],
#   TPR = m11_perf_external@y.values[[1]],
#   cutoff = m11_perf_external@alpha.values[[1]])
# 
# # las resultas
#   #coef(m11_logit_all_factor$finalModel)
# m11_logit_all_factor$results$ROC
# m11_AUC_test
# m11_AUC_external

```

m12_logit_penalized_facor
```{r}
# test data
m12_test_pred <- predict.train(m12_logit_penalized_facor, newdata = JZ_test, type = "prob")
m12_pred_test <- prediction(m12_test_pred$Y, JZ_test[["f_Target"]])
m12_perf_test <- performance(m12_pred_test, measure = "tpr", x.measure = "fpr")
m12_AUC_test <- performance(m12_pred_test, measure = "auc")@y.values[[1]]
m12_roc_df_test <- data.table(
  model = "m12_logit_penalized_facor",
  FPR = m12_perf_test@x.values[[1]],
  TPR = m12_perf_test@y.values[[1]],
  cutoff = m12_perf_test@alpha.values[[1]])

# external data
m12_external_pred <- predict.train(m12_logit_penalized_facor, newdata = JZ_external, type = "prob")
m12_pred_external <- prediction(m12_external_pred$Y, JZ_external[["f_Target"]])
m12_perf_external <- performance(m12_pred_external, measure = "tpr", x.measure = "fpr")
m12_AUC_external <- performance(m12_pred_external, measure = "auc")@y.values[[1]]
m12_roc_df_external <- data.table(
  model = "m12_logit_penalized_facor",
  FPR = m12_perf_external@x.values[[1]],
  TPR = m12_perf_external@y.values[[1]],
  cutoff = m12_perf_external@alpha.values[[1]])

# las resultas
  #coef(m12_logit_penalized_facor$finalModel)
m12_logit_penalized_facor$results$ROC
m12_AUC_test
m12_AUC_external


```

m13_rpart_factor
```{r}
# test data
m13_test_pred <- predict.train(m13_rpart_factor, newdata = JZ_test, type = "prob")
m13_pred_test <- prediction(m13_test_pred$Y, JZ_test[["f_Target"]])
m13_perf_test <- performance(m13_pred_test, measure = "tpr", x.measure = "fpr")
m13_AUC_test <- performance(m13_pred_test, measure = "auc")@y.values[[1]]
m13_roc_df_test <- data.table(
  model = "m13_rpart_factor",
  FPR = m13_perf_test@x.values[[1]],
  TPR = m13_perf_test@y.values[[1]],
  cutoff = m13_perf_test@alpha.values[[1]])

# external data
m13_external_pred <- predict.train(m13_rpart_factor, newdata = JZ_external, type = "prob")
m13_pred_external <- prediction(m13_external_pred$Y, JZ_external[["f_Target"]])
m13_perf_external <- performance(m13_pred_external, measure = "tpr", x.measure = "fpr")
m13_AUC_external <- performance(m13_pred_external, measure = "auc")@y.values[[1]]
m13_roc_df_external <- data.table(
  model = "m13_rpart_factor",
  FPR = m13_perf_external@x.values[[1]],
  TPR = m13_perf_external@y.values[[1]],
  cutoff = m13_perf_external@alpha.values[[1]])

# las resultas
m13_rpart_factor$results$ROC
m13_AUC_test
m13_AUC_external
```

m14_RF_factor
```{r}
# test data
m14_test_pred <- predict.train(m14_RF_factor, newdata = JZ_test, type = "prob")
m14_pred_test <- prediction(m14_test_pred$Y, JZ_test[["f_Target"]])
m14_perf_test <- performance(m14_pred_test, measure = "tpr", x.measure = "fpr")
m14_AUC_test <- performance(m14_pred_test, measure = "auc")@y.values[[1]]
m14_roc_df_test <- data.table(
  model = "m14_RF_factor",
  FPR = m14_perf_test@x.values[[1]],
  TPR = m14_perf_test@y.values[[1]],
  cutoff = m14_perf_test@alpha.values[[1]])

# external data
m14_external_pred <- predict.train(m14_RF_factor, newdata = JZ_external, type = "prob")
m14_pred_external <- prediction(m14_external_pred$Y, JZ_external[["f_Target"]])
m14_perf_external <- performance(m14_pred_external, measure = "tpr", x.measure = "fpr")
m14_AUC_external <- performance(m14_pred_external, measure = "auc")@y.values[[1]]
m14_roc_df_external <- data.table(
  model = "m14_RF_factor",
  FPR = m14_perf_external@x.values[[1]],
  TPR = m14_perf_external@y.values[[1]],
  cutoff = m14_perf_external@alpha.values[[1]])

# las resultas
varImp(m14_RF_factor, scale = FALSE)
m14_RF_factor$results$ROC
m14_AUC_test
m14_AUC_external
    ```

m15_pcr_factor
```{r}
# test data
m15_test_pred <- predict.train(m15_pcr_factor, newdata = JZ_test, type = "prob")
m15_pred_test <- prediction(m15_test_pred$Y, JZ_test[["f_Target"]])
m15_perf_test <- performance(m15_pred_test, measure = "tpr", x.measure = "fpr")
m15_AUC_test <- performance(m15_pred_test, measure = "auc")@y.values[[1]]
m15_roc_df_test <- data.table(
  model = "m15_pcr_factor",
  FPR = m15_perf_test@x.values[[1]],
  TPR = m15_perf_test@y.values[[1]],
  cutoff = m15_perf_test@alpha.values[[1]])

m15_external_pred <- predict.train(m15_pcr_factor, newdata = JZ_external, type = "prob")
m15_pred_external <- prediction(m15_external_pred$Y, JZ_external[["f_Target"]])
m15_perf_external <- performance(m15_pred_external, measure = "tpr", x.measure = "fpr")
m15_AUC_external <- performance(m15_pred_external, measure = "auc")@y.values[[1]]
m15_roc_df_external <- data.table(
  model = "m15_pcr_factor",
  FPR = m15_perf_external@x.values[[1]],
  TPR = m15_perf_external@y.values[[1]],
  cutoff = m15_perf_external@alpha.values[[1]])

# las resultas
#coef(m15_pcr_factor$finalModel)
m15_pcr_factor$results$ROC
m15_AUC_test
m15_AUC_external
```

m16_GBM_factor
```{r}
# test data
m16_test_pred <- predict.train(m16_GBM_factor, newdata = JZ_test, type = "prob")
m16_pred_test <- prediction(m16_test_pred$Y, JZ_test[["f_Target"]])
m16_perf_test <- performance(m16_pred_test, measure = "tpr", x.measure = "fpr")
m16_AUC_test <- performance(m16_pred_test, measure = "auc")@y.values[[1]]
m16_roc_df_test <- data.table(
  model = "m16_GBM_factor",
  FPR = m16_perf_test@x.values[[1]],
  TPR = m16_perf_test@y.values[[1]],
  cutoff = m16_perf_test@alpha.values[[1]])

m16_external_pred <- predict.train(m16_GBM_factor, newdata = JZ_external, type = "prob")
m16_pred_external <- prediction(m16_external_pred$Y, JZ_external[["f_Target"]])
m16_perf_external <- performance(m16_pred_external, measure = "tpr", x.measure = "fpr")
m16_AUC_external <- performance(m16_pred_external, measure = "auc")@y.values[[1]]
m16_roc_df_external <- data.table(
  model = "m16_GBM_factor",
  FPR = m16_perf_external@x.values[[1]],
  TPR = m16_perf_external@y.values[[1]],
  cutoff = m16_perf_external@alpha.values[[1]])

# las resultas
#coef(m16_GBM_factor$finalModel)
m16_GBM_factor$results$ROC
m16_AUC_test
m16_AUC_external
```


##1w log

m20_logit_base_log
```{r}
# test data
m20_test_pred <- predict.train(m20_logit_base_log, newdata = JZ_test, type = "prob")
m20_pred_test <- prediction(m20_test_pred$Y, JZ_test[["f_Target"]])
m20_perf_test <- performance(m20_pred_test, measure = "tpr", x.measure = "fpr")
m20_AUC_test <- performance(m20_pred_test, measure = "auc")@y.values[[1]]
m20_roc_df_test <- data.table(
  model = "m20_logit_base_log",
  FPR = m20_perf_test@x.values[[1]],
  TPR = m20_perf_test@y.values[[1]],
  cutoff = m20_perf_test@alpha.values[[1]])

# external data
m20_external_pred <- predict.train(m20_logit_base_log, newdata = JZ_external, type = "prob")
m20_pred_external <- prediction(m20_external_pred$Y, JZ_external[["f_Target"]])
m20_perf_external <- performance(m20_pred_external, measure = "tpr", x.measure = "fpr")
m20_AUC_external <- performance(m20_pred_external, measure = "auc")@y.values[[1]]
m20_roc_df_external <- data.table(
  model = "m20_logit_base_log",
  FPR = m20_perf_external@x.values[[1]],
  TPR = m20_perf_external@y.values[[1]],
  cutoff = m20_perf_external@alpha.values[[1]])

# las resultas
  # coef(m20_logit_base_log$finalModel)
m20_logit_base_log$results$ROC
m20_AUC_test
m20_AUC_external

```


m21_logit_all_log
```{r}
# # test data
# m21_test_pred <- predict.train(m21_logit_all_log, newdata = JZ_test, type = "prob")
# m21_pred_test <- prediction(m21_test_pred$Y, JZ_test[["f_Target"]])
# m21_perf_test <- performance(m21_pred_test, measure = "tpr", x.measure = "fpr")
# m21_AUC_test <- performance(m21_pred_test, measure = "auc")@y.values[[1]]
# m21_roc_df_test <- data.table(
#   model = "m21_logit_all_log",
#   FPR = m21_perf_test@x.values[[1]],
#   TPR = m21_perf_test@y.values[[1]],
#   cutoff = m21_perf_test@alpha.values[[1]])
# 
# # external data
# m21_external_pred <- predict.train(m21_logit_all_log, newdata = JZ_external, type = "prob")
# m21_pred_external <- prediction(m21_external_pred$Y, JZ_external[["f_Target"]])
# m21_perf_external <- performance(m21_pred_external, measure = "tpr", x.measure = "fpr")
# m21_AUC_external <- performance(m21_pred_external, measure = "auc")@y.values[[1]]
# m21_roc_df_external <- data.table(
#   model = "m21_logit_all_log",
#   FPR = m21_perf_external@x.values[[1]],
#   TPR = m21_perf_external@y.values[[1]],
#   cutoff = m21_perf_external@alpha.values[[1]])
# 
# # las resultas
#   #coef(m21_logit_all_log$finalModel)
# m21_logit_all_log$results$ROC
# m21_AUC_test
# m21_AUC_external

```

m22_logit_penalized_log
```{r}
# test data
m22_test_pred <- predict.train(m22_logit_penalized_log, newdata = JZ_test, type = "prob")
m22_pred_test <- prediction(m22_test_pred$Y, JZ_test[["f_Target"]])
m22_perf_test <- performance(m22_pred_test, measure = "tpr", x.measure = "fpr")
m22_AUC_test <- performance(m22_pred_test, measure = "auc")@y.values[[1]]
m22_roc_df_test <- data.table(
  model = "m22_logit_penalized_log",
  FPR = m22_perf_test@x.values[[1]],
  TPR = m22_perf_test@y.values[[1]],
  cutoff = m22_perf_test@alpha.values[[1]])

# external data
m22_external_pred <- predict.train(m22_logit_penalized_log, newdata = JZ_external, type = "prob")
m22_pred_external <- prediction(m22_external_pred$Y, JZ_external[["f_Target"]])
m22_perf_external <- performance(m22_pred_external, measure = "tpr", x.measure = "fpr")
m22_AUC_external <- performance(m22_pred_external, measure = "auc")@y.values[[1]]
m22_roc_df_external <- data.table(
  model = "m22_logit_penalized_log",
  FPR = m22_perf_external@x.values[[1]],
  TPR = m22_perf_external@y.values[[1]],
  cutoff = m22_perf_external@alpha.values[[1]])

# las resultas
  #coef(m22_logit_penalized_log$finalModel)
m22_logit_penalized_log$results$ROC
m22_AUC_test
m22_AUC_external
```

m23_rpart_log
```{r}
# test data
m23_test_pred <- predict.train(m23_rpart_log, newdata = JZ_test, type = "prob")
m23_pred_test <- prediction(m23_test_pred$Y, JZ_test[["f_Target"]])
m23_perf_test <- performance(m23_pred_test, measure = "tpr", x.measure = "fpr")
m23_AUC_test <- performance(m23_pred_test, measure = "auc")@y.values[[1]]
m23_roc_df_test <- data.table(
  model = "m23_rpart_log",
  FPR = m23_perf_test@x.values[[1]],
  TPR = m23_perf_test@y.values[[1]],
  cutoff = m23_perf_test@alpha.values[[1]])

# external data
m23_external_pred <- predict.train(m23_rpart_log, newdata = JZ_external, type = "prob")
m23_pred_external <- prediction(m23_external_pred$Y, JZ_external[["f_Target"]])
m23_perf_external <- performance(m23_pred_external, measure = "tpr", x.measure = "fpr")
m23_AUC_external <- performance(m23_pred_external, measure = "auc")@y.values[[1]]
m23_roc_df_external <- data.table(
  model = "m23_rpart_log",
  FPR = m23_perf_external@x.values[[1]],
  TPR = m23_perf_external@y.values[[1]],
  cutoff = m23_perf_external@alpha.values[[1]])

# las resultas
m23_rpart_log$results$ROC
m23_AUC_test
m23_AUC_external
```

m24_RF_log
```{r}
# test data
m24_test_pred <- predict.train(m24_RF_log, newdata = JZ_test, type = "prob")
m24_pred_test <- prediction(m24_test_pred$Y, JZ_test[["f_Target"]])
m24_perf_test <- performance(m24_pred_test, measure = "tpr", x.measure = "fpr")
m24_AUC_test <- performance(m24_pred_test, measure = "auc")@y.values[[1]]
m24_roc_df_test <- data.table(
  model = "m24_RF_log",
  FPR = m24_perf_test@x.values[[1]],
  TPR = m24_perf_test@y.values[[1]],
  cutoff = m24_perf_test@alpha.values[[1]])

# external data
m24_external_pred <- predict.train(m24_RF_log, newdata = JZ_external, type = "prob")
m24_pred_external <- prediction(m24_external_pred$Y, JZ_external[["f_Target"]])
m24_perf_external <- performance(m24_pred_external, measure = "tpr", x.measure = "fpr")
m24_AUC_external <- performance(m24_pred_external, measure = "auc")@y.values[[1]]
m24_roc_df_external <- data.table(
  model = "m24_RF_log",
  FPR = m24_perf_external@x.values[[1]],
  TPR = m24_perf_external@y.values[[1]],
  cutoff = m24_perf_external@alpha.values[[1]])

# las resultas
varImp(m24_RF_log, scale = FALSE)
m24_RF_log$results$ROC
m24_AUC_test
m24_AUC_external
```

m25_pcr_log
```{r}
# test data
m25_test_pred <- predict.train(m25_pcr_log, newdata = JZ_test, type = "prob")
m25_pred_test <- prediction(m25_test_pred$Y, JZ_test[["f_Target"]])
m25_perf_test <- performance(m25_pred_test, measure = "tpr", x.measure = "fpr")
m25_AUC_test <- performance(m25_pred_test, measure = "auc")@y.values[[1]]
m25_roc_df_test <- data.table(
  model = "m25_pcr_log",
  FPR = m25_perf_test@x.values[[1]],
  TPR = m25_perf_test@y.values[[1]],
  cutoff = m25_perf_test@alpha.values[[1]])

m25_external_pred <- predict.train(m25_pcr_log, newdata = JZ_external, type = "prob")
m25_pred_external <- prediction(m25_external_pred$Y, JZ_external[["f_Target"]])
m25_perf_external <- performance(m25_pred_external, measure = "tpr", x.measure = "fpr")
m25_AUC_external <- performance(m25_pred_external, measure = "auc")@y.values[[1]]
m25_roc_df_external <- data.table(
  model = "m25_pcr_log",
  FPR = m25_perf_external@x.values[[1]],
  TPR = m25_perf_external@y.values[[1]],
  cutoff = m25_perf_external@alpha.values[[1]])

# las resultas
#coef(m25_pcr_log$finalModel)
m25_pcr_log$results$ROC
m25_AUC_test
m25_AUC_external
```

m26_GBM_log
```{r}
# test data
m26_test_pred <- predict.train(m26_GBM_log, newdata = JZ_test, type = "prob")
m26_pred_test <- prediction(m26_test_pred$Y, JZ_test[["f_Target"]])
m26_perf_test <- performance(m26_pred_test, measure = "tpr", x.measure = "fpr")
m26_AUC_test <- performance(m26_pred_test, measure = "auc")@y.values[[1]]
m26_roc_df_test <- data.table(
  model = "m26_GBM_log",
  FPR = m26_perf_test@x.values[[1]],
  TPR = m26_perf_test@y.values[[1]],
  cutoff = m26_perf_test@alpha.values[[1]])

m26_external_pred <- predict.train(m26_GBM_log, newdata = JZ_external, type = "prob")
m26_pred_external <- prediction(m26_external_pred$Y, JZ_external[["f_Target"]])
m26_perf_external <- performance(m26_pred_external, measure = "tpr", x.measure = "fpr")
m26_AUC_external <- performance(m26_pred_external, measure = "auc")@y.values[[1]]
m26_roc_df_external <- data.table(
  model = "m26_GBM_log",
  FPR = m26_perf_external@x.values[[1]],
  TPR = m26_perf_external@y.values[[1]],
  cutoff = m26_perf_external@alpha.values[[1]])

# las resultas
#coef(m26_GBM_log$finalModel)
m26_GBM_log$results$ROC
m26_AUC_test
m26_AUC_external
```


deleting what is not needed
```{r}
rm(m00_test_pred, m00_pred_test, m00_perf_test, m00_external_pred, m00_pred_external, m00_perf_external)
rm(m02_test_pred, m02_pred_test, m02_perf_test, m02_external_pred, m02_pred_external, m02_perf_external)
rm(m04_test_pred, m04_pred_test, m04_perf_test, m04_external_pred, m04_pred_external, m04_perf_external)
rm(m05_test_pred, m05_pred_test, m05_perf_test, m05_external_pred, m05_pred_external, m05_perf_external)
rm(m06_test_pred, m06_pred_test, m06_perf_test, m06_external_pred, m06_pred_external, m06_perf_external)
rm(m10_test_pred, m10_pred_test, m10_perf_test, m10_external_pred, m10_pred_external, m10_perf_external)
rm(m12_test_pred, m12_pred_test, m12_perf_test, m12_external_pred, m12_pred_external, m12_perf_external)
rm(m14_test_pred, m14_pred_test, m14_perf_test, m14_external_pred, m14_pred_external, m14_perf_external)
rm(m15_test_pred, m15_pred_test, m15_perf_test, m15_external_pred, m15_pred_external, m15_perf_external)
rm(m16_test_pred, m16_pred_test, m16_perf_test, m16_external_pred, m16_pred_external, m16_perf_external)
rm(m20_test_pred, m20_pred_test, m20_perf_test, m20_external_pred, m20_pred_external, m20_perf_external)
rm(m22_test_pred, m22_pred_test, m22_perf_test, m22_external_pred, m22_pred_external, m22_perf_external)
rm(m24_test_pred, m24_pred_test, m24_perf_test, m24_external_pred, m24_pred_external, m24_perf_external)
rm(m25_test_pred, m25_pred_test, m25_perf_test, m25_external_pred, m25_pred_external, m25_perf_external)
rm(m26_test_pred, m26_pred_test, m26_perf_test, m26_external_pred, m26_pred_external, m26_perf_external)
```



